Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-12-15 minimax.tex
new figures

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}

@@

\paragraph{Comparison of strategies}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
	\includegraphics[width=.45\textwidth]{comparison.png}
\end{figure}
\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		50	&15.96	&0.54	&17.26	&0.42\\
		100	&12.48	&0.93	&15.6	&0.43\\
		150	&9.58	&1.37	&13.94	&0.76\\
		200	&7.43	&1.25	&10.95	&1.12\\
		250	&5.26	&1.52	&6.6	&0.79\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.

@@

%\subsection{Decrease in MMR values}
\paragraph{Decrease in MMR values}
\begin{figure}
	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
	\includegraphics[width=.45\textwidth]{linearity.png}
\end{figure}

>>>>

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}

@@

\paragraph{Comparison of strategies}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
	\begin{tikzpicture}
		\begin{axis}[
			y=10,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			ytick={0,2,4,6,8,10,12},
			xtick distance=10,
			ytick distance=2,
			xtick pos=left,
			ymajorgrids=true,
			ytick style={draw=none},
			ymin=0,
			ymax=12,
			xmin=0,
			xmax=100,
			yticklabels={0,2,4,6,8,10,12}]
			\addlegendimage{mark=*,teal,mark size=2}
			\addlegendimage{mark=triangle*,orange,mark size=2}
			\addlegendimage{mark=square*,blue,mark size=2}
			\addlegendimage{mark=diamond*,red,mark size=2}

			\addplot[thick, mark=*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=Pes.]{data/comparison.dat};
			\addlegendentry{Pes.}
			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {45}, orange] table [x=k, y=Ex.Pes.]{data/comparison.dat};
			\addlegendentry{Ex.Pes.}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {50}, blue] table [x=k, y=Eli.]{data/comparison.dat};
			\addlegendentry{Eli.}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {50}, red] table [x=k, y=Rnd.]{data/comparison.dat};
			\addlegendentry{Rnd.}

		\end{axis}
	\end{tikzpicture}
\end{figure}

%\begin{figure}
%	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
%	\label{fig:smallSize}
%%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
%	\includegraphics[width=.45\textwidth]{comparison.png}
%\end{figure}
\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		50	&15.96	&0.54	&17.26	&0.42\\
		100	&12.48	&0.93	&15.6	&0.43\\
		150	&9.58	&1.37	&13.94	&0.76\\
		200	&7.43	&1.25	&10.95	&1.12\\
		250	&5.26	&1.52	&6.6	&0.79\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.

@@

%\subsection{Decrease in MMR values}
\paragraph{Decrease in MMR values}

\begin{figure}
	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	\begin{tikzpicture}
		\pgfplotsset{
			every axis legend/.append style={
				at={(0.5,1.03)},
				anchor=south
			},
		}
		\begin{axis}[
			y=3.5,
			legend columns=3,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			ytick={0,5,10,15,20,25,30,35},
			xtick distance=100,
			ytick distance=5,
			xtick pos=left,
			ymajorgrids=true,
			ytick style={draw=none},
			ymin=0,
			ymax=35,
			xmin=0,
			xmax=800,
			yticklabels={0,5,10,15,20,25,30,35}]

			\addlegendimage{mark=triangle*,teal,mark size=2}
			\addlegendimage{mark=*,violet,mark size=2}
			\addlegendimage{mark=square*,green,mark size=2}
			\addlegendimage{mark=diamond*,red,mark size=2}
			\addlegendimage{mark=pentagon*,cyan,mark size=2}
			\addlegendimage{mark=halfsquare*,magenta,mark size=2}

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
			\addlegendentry{m=5, n=10}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
			\addlegendentry{m=15, n=30}
		\end{axis}
	\end{tikzpicture}
\end{figure}
%\begin{figure}
%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
%
%	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
%	\includegraphics[width=.45\textwidth]{linearity.png}
%\end{figure}
